### 2023-02-02 README.Rmd
CRAN 0.6

@@

**cols4all** will be available on CRAN in January or February this year (2023). Until then it can be installed using:

```{r, eval=FALSE}
# colorspace 2.1 required:
install.packages("colorspace", repos = "https://R-Forge.R-project.org")

# development (github) version of cols4all
install.packages("remotes")
remotes::install_github("mtennekes/cols4all", dependencies = TRUE)
```

>>>>

[![CRAN](http://www.r-pkg.org/badges/version/cols4all)](https://cran.r-project.org/package=cols4all) 
[![cran checks](https://cranchecks.info/badges/worst/cols4all)](https://cran.r-project.org/web/checks/check_results_cols4all.html)
[![Downloads](http://cranlogs.r-pkg.org/badges/cols4all?color=brightgreen)](http://www.r-pkg.org/pkg/cols4all)

@@

**cols4all** is available on CRAN:

```{r, eval=FALSE}
install.packages("cols4all", dependencies = TRUE)
```

The development version can be installed as follows:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("mtennekes/cols4all", dependencies = TRUE)
```
